---
title: "546_R_HW"
author: "Laurel Nave-Powers"
date: "2/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## This homework involves writing a script that performs a task on a number of files. 
## When you trim the adaptors from raw reads, you also get supplemental materials as output. My script will take the tables in the supplemental files and combine them into one. 

## First, read in the data and name each file. 
```{r}
hipplat_1 <- read.csv("../data/HIPPLAT_NEF95054_S2_R1_supp_table.csv")
hipplat_2 <- read.csv("../data/HIPPLAT_NEF95054_S2_R2_supp_table.csv")
micpaci_1 <- read.csv("../data/MICPACI_UW157426_S7_R1_supp_table.csv")
micpaci_2 <- read.csv("../data/MICPACI_UW157426_S7_R2_supp_table.csv")
```
## Let's take a look at what some of the data looks like by using head. 
```{r}
head(hipplat_1)
```
## Now that the data is read in and we have an idea of what it looks like and what the column headings are, we can combine them. 
```{r}
combined <- c(hipplat_1, hipplat_2, micpaci_1, micpaci_2)
head(combined) 
```